Evaluating a lightweight transcriptome assembly pipeline on two closely related ascidian species

### 2015-09-14 manuscript/main.tex
fixed numbers in relation to figure two

\subsection{Assembly statistics varied by preprocessing approach and assembler}
Oases run with the diginormed reads yielded fewer total transcripts than Oases run with the unnormalized reads. The \textit{M. oculata} diginorm assembly produced 300 fewer transcripts, and the \textit{M. occulta} diginorm assembly produced 227 fewer transcripts (Table~\ref{table:Table2.pdf}). Digital normalization had the opposite affect when using Trinity for assembly, increasing the total number of assembled transcripts by 7,840 for \textit{M. oculata} and 9,197 for \textit{M. occulta}.

@@

Trinity produces 6.8k (7.6\%) more transcripts than Oases for \textit{M. occulta} using the digitally normalized reads, and a 2.6k (2.9\%) decrease in the number of transcripts using the unnormalized reads. Trinity assembled more transcripts for both \textit{M. oculata} assemblies, a 17.6k (44.8\%) increase for diginorm and a 9.5k (24\%) increase for the raw reads.

>>>>

\subsection{Assembly statistics varied by preprocessing approach and assembler}
Oases run with the diginormed reads yielded fewer total transcripts than Oases run with the unnormalized reads. The \textit{M. oculata} diginorm assembly produced 490 fewer transcripts, and the \textit{M. occulta} diginorm assembly produced 2,899 fewer transcripts (Table~\ref{table:Table2.pdf}). Digital normalization had the opposite affect when using Trinity for assembly, increasing the total number of assembled transcripts by 17,688 for \textit{M. oculata} and 13,611 for \textit{M. occulta}.

@@

Trinity produces 23.5k (30.4\%) more transcripts than Oases for \textit{M. occulta} using the digitally normalized reads, and a 6.9k (8.7\%) increase in the number of transcripts using the unnormalized reads. Trinity assembled more transcripts for both \textit{M. oculata} assemblies, a 28.8k (75\%) increase for diginorm and a 10.6k (27.3\%) increase for the raw reads compared to the oases assemblies.
